The \dealii Library, Version 9.5

### 2023-06-29 9.5/paper.tex
Extend info

\item Several old interfaces to \texttt{MatrixFree} have been removed, e.g.,
  initialization functions without \texttt{Mapping} argument and the query
  to the number of cell batches. In
  each case, new interfaces are available.
\end{itemize}

>>>>

\item Several old interfaces to \texttt{MatrixFree} have been removed, e.g.,
  initialization functions without \texttt{Mapping} argument and some queries
  to the number of cell batches as well as \texttt{DoFHandler} objects. In
  each case, new interfaces are available.
\end{itemize}
